Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-01-30 inst/examples/20170125-Manuscript-FK.Rmd
analysis update

@@

dfs <- df %>% select(publication_decade, publisher) %>% unique
p <- plot_timeline(dfs, x = "publication_decade") +
     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
print(p)

```

>>>>

### Kungliga / Linkoping

@@

dfs <- df %>% select(publication_decade, publisher) %>% unique
p <- plot_timeline(dfs, x = "publication_decade") +
     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
print(p)    
```
